biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-09-27 paper/PaperTRA/PaperTRA.Rmd
bug values TP total
try to understand why there are only max new 104k trips in scenario 3, but there are 224k trips that can be replaced cyc + TP

The intermodality scenario considers trips combining PT and cycling for the first and last legs.
In a conservative approach, we have restricted our analysis to the first and last legs with a combined length of up to 5 km or up to 25 minutes on bike.
Furthermore, we have imposed restrictions on PT usage to include only trips with no PT transfers, and up to 2 hours (120 min).
Additionally, we have only included PT modes that can easily accommodate bicycles, such as trains, ferries, trams, and inter-municipal bus lines equipped with bike racks (Figure \ref{fig:map1}).

@@

Table \ref{tab:summary1} presents the LMA total daily trips, the cycling combined with PT trips in the baseline scenario and corresponding potential trips to achieve the national strategy targets (4% and 10%), for different route profiles. 
For the cycling legs of the journey (first and last legs), the environmental avoided emmissions and monetized socio-environment benefits are also presented, resulting from replacing car trips with cycling.

For both *direct* and *safe* route profiles, 20% of the daily car trips have the potential to be replaced by a combination of PT and cycling (up to 5 km on bike).

<!-- Meta ENMAC Cenário Tipo de Percurso    Total Viagens /dia  Viagens Bicicleta Base  Viagens Bicicleta Potencial CO~2~eq evitado (ton/ano)   Benefícios estimados em 10 anos (milhares €) -->

<!-- 4% intermodal até 5km  seguro  1 077 028   4 624   40 770  5 920   230 270 -->

<!-- 4% intermodal até 5km  direto  1 001 761   4 547   37 889  6 011   223 720 -->

<!-- 10%    intermodal até 5km  seguro  1 077 028   4 624   104 647 15 192  591 790 -->

<!-- 10%    intermodal até 5km  direto  1 001 761   4 547   97 218  15 414  574 200 -->

@@

knitr::kable(summary1,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total trips",
                    "Baseline Cycling + PT", "Potencial Cycling + PT",
                    "Avoided CO2eq (ton/yr)", "SE Benefits for 10 years (thousand €)"),
      caption = "\\label{summary1old}Summary of the cycling potencial of intermodality scenario.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(4:7), width = "6em")
  # kableExtra::kable_styling(full_width = TRUE)

@@

This scenario unveils the potential of bicycles as a complementary mode of PT, with the prospective to uptake the number of PT trips within the LMA area by as much as 12% (in addition to the 825,000 reported in the mobility survey).
These findings indicate that transferring car trips to a combination of bicycle and PT could be nearly as substantial, if not equally significant, as the shift towards bicycle-only trips.

@@

```{r summary2, out.width="100%", fig.cap="Potencial de transferência estimado para cada modo de transporte público, bem como as estimativas de consumo de CO~2~eq evitado anualmente por transferência do automóvel."}
knitr::include_graphics("img/table2.png", error = FALSE)
```

>>>>

The intermodality scenario considers trips combining PT and cycling for the first and last legs.
In a conservative approach, we have restricted our analysis to the first and last legs with a combined length of up to 5 km (for instance: 1 km from origin to interface A plus 4 km from interface B to destination) or up to 25 minutes on bike.
Furthermore, we have imposed restrictions on PT usage to include only trips with no PT transfers, and up to 2 hours (120 min).
Additionally, we have only included PT modes that can easily accommodate bicycles, such as trains, ferries, trams, and inter-municipal bus lines equipped with bike racks (Figure \ref{fig:map1}).

@@

Table \ref{tab:summary1} presents the LMA total daily trips, the cycling combined with PT trips in the baseline scenario and corresponding new trips to achieve the national strategy targets (4% and 10%), for different route profiles. 
For the cycling legs of the journey (first and last legs), the environmental avoided emmissions and monetized socio-environment benefits are also presented, resulting from replacing car trips with cycling.

For both *direct* and *safe* route profiles, 20% of the daily car trips have the potential to be replaced by a combination of PT and cycling (up to 5 km on bike). 
<!-- place in the end - here is not clear -->

@@

knitr::kable(summary1,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total trips",
                    "Baseline Cycling + PT", "Potencial Cycling + PT",
                    "Avoided CO2eq (ton/yr)", "SE Benefits for 10 years (thousand €)"),
      caption = "\\label{summary1}Summary of the cycling potencial of intermodality scenario.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(4:7), width = "6em")
  # kableExtra::kable_styling(full_width = TRUE)

@@

This scenario unveils the potential of bicycles as a complementary mode of PT, with the potential to uptake the number of PT trips within the LMA area by as much as 12% (in addition to the 825,000 reported in the mobility survey).
These findings indicate that transferring car trips to a combination of bicycle and PT could be nearly as substantial, if not equally significant, as the shift towards bicycle-only trips.

@@

Table \ref{tab:summary21} shows something that doesn't make sense.
<!-- ???? -->

```{r summary2old, eval=FALSE, out.width="100%", fig.cap="Potencial de transferência estimado para cada modo de transporte público, bem como as estimativas de consumo de CO~2~eq evitado anualmente por transferência do automóvel."}
knitr::include_graphics("img/table2.png", error = FALSE)
```

```{r summary21}
summary2 = readRDS("load/TPtable_aml.Rds")

summary21 = summary2 %>%
  mutate(LTS = recode(Percursos, "seguro" = "safe", "direto" = "direct")) |> 
  select(Meta_ENMAC, LTS, Total, BUS, FERRY, RAIL, TRAM)

knitr::kable(summary21,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total",
                    "Bus", "Ferry", "Train", "Tram"),
      caption = "\\label{summary21}Summary of the potential of replacing car trips with cycling in combination with PT, disagregated by PT mode.",
      format="latex",
      booktabs = TRUE)
  # kableExtra::column_spec(column = c(4:7), width = "6em")
  # kableExtra::kable_styling(full_width = TRUE)

```{r summary22}

summary22 = summary2 %>%
  mutate(LTS = recode(Percursos, "seguro" = "safe", "direto" = "direct")) |> 
  select(Meta_ENMAC, LTS, CO2eq_TP, CO_PT, PM10_PT, NOx_PT, VOC_PT, money_emissions_eur)
```
